--- 
title: "YATA Technical Manual"
author: "Javier Gonzalez"
date: "`r Sys.Date()`"
bibliography:
- book.bib
- packages.bib
description: This is a minimal example of using the bookdown package to write a book.
  The output format for this example is bookdown::gitbook.
documentclass: book
link-citations: yes
site: bookdown::bookdown_site
biblio-style: apalike
config:
  sharing: null
output: 
  html_document: 
    toc: yes
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
library(abind)
library(png)
library(grid)

# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

```{r, echo=FALSE}
colorize <- function(color, x) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
      x)
  } else x
}
```